New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-04 Manuscript/Manuscript.Rmd
Continue with M&M

The objective of this work is twofold: 1) estimate the interaction strength of the Weddell Sea food web, and 2) 
determine key trophic species considering its influence on the stability of the network.

@@

## Data source

Subsubsection text here.

@@

You can ad \LaTeX table in an R Markdown document to meet the template
requirements.

>>>>

The objective of this work was twofold: 1) estimate the strength for each interaction in the Weddell Sea food web, and 2) determine key trophic species considering weighted and unweighted properties and the influence on the stability of the network.

@@

Add Figure of map.

## Weddell Sea food web data set

We obtained the data set of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018].
This marine food web, which includes all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, is one of the most highly resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

## Data set analyses

Text here.

### Interaction strength estimation

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012.

### Species properties

In order to characterize the species, we considered weighted and unweighted properties. The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991, @Dunne2002, @Borrelli2014]. As weighted property we used the mean interaction strength, meaning the average strength of all species interactions. As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.

Add Figure of toy food web.

### Stability and extinction simulations

Quasi-Sign Stability (QSS) [@Allesina2008].
After each species extinction, we calculated the QSS for the food web minus one species and compared it with the QSS for the whole network. We statistically analysed such difference applying the Anderson-Darling test [@Scholz1987].

@@

You can add \LaTeX table in an R Markdown document to meet the template
requirements.

### 2022-08-04 Manuscript/Manuscript.tex
Continue with M&M

\subsection{Data source}

Subsubsection text here.

>>>>

Add Figure of map.

\subsection{Weddell Sea food web data set}

We obtained the data set of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This marine food web, which
includes all the food web data available for the high Antarctic Weddell
Sea collected since 1983, is one of the most highly resolved marine food
webs documented to date. It's noteworthy that it is a summary network
that ignores seasonal changes \citep{Jacob2011}.

\subsection{Data set analyses}

Text here.

\subsubsection{Interaction strength estimation}

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}.

\subsubsection{Species properties}

In order to characterize the species, we considered weighted and
unweighted properties. The former is based on the estimation of the
interaction strength described in the previous section. The latter is
related to properties commonly used in qualitative (presence/absence of
interaction) food web studies \citep[\citet{Dunne2002},
\citet{Borrelli2014}]{Martinez1991}. As weighted property we used the
mean interaction strength, meaning the average strength of all species
interactions. As unweighted properties we used: a) degree or the total
number of trophic interactions taking into account in- and
out-interactions (role as predator and prey, respectively); b) trophic
level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the measurement of
trophic overlap between species based on shared and unique resources and
consumers.

Add Figure of toy food web.

\subsubsection{Stability and extinction simulations}

Quasi-Sign Stability (QSS) \citep{Allesina2008}. After each species
extinction, we calculated the QSS for the food web minus one species and
compared it with the QSS for the whole network. We statistically
analysed such difference applying the Anderson-Darling test
\citep{Scholz1987}.
